Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-06 paper.qmd
Updated Figure 14 with optimal bin widths

<!--Fit the best model for author suggestion and compute error-->
```{r}
#| label: hexbin-pbmc
## Compute hexbin parameters
num_bins_x_pbmc <- 21

@@

distance_df_small_edges_pbmc <- distance_pbmc |>
  filter(distance < 0.06)#benchmark_pbmc

>>>>

<!--Fit the best model for author suggestion and compute error-->
```{r}
#| label: hexbin-pbmc
## Compute hexbin parameters
num_bins_x_pbmc <- 22

@@

distance_df_small_edges_pbmc <- distance_pbmc |>
  filter(distance < benchmark_pbmc)#benchmark_pbmc
